The Countercyclical Component of Capital Regulation

### 2021-04-23 Analysis/Draft/Draft_bookdown.Rmd
version dissertation pre defense

---
title: "The Countercyclical Component of Capital Regulation"
date: '\emph{\today}'
output:
  bookdown::pdf_document2:
    fig_caption: yes
    #citation_package: natbib
    latex_engine: pdflatex
    template: tex-ms.tex
  pdf_document: default
  word_document: default
author:
- name: "Lucas Avezum"
  affiliation: "CentER and EBC, Tilburg University"
biblio-style: apsr
bibliography: ../../Auxiliar/mybibfile.bib
citecolor: black
csl: ../../Auxiliar/Citation_styles/american-marketing-association.csl
#anonymous: no
fontsize: 11pt
geometry: margin= 1in
header-includes: \usepackage{rotating, graphicx, dcolumn, longtable, float, siunitx, tabularx, appendix} 
keywords: Internal ratings-based models, Risk-weighted assets dispersion, Procyclicality
linkcolor: black
abstract: The Basel II accord introduced a concave mapping from probabilities of default
  (PD) to capital requirements for banks adopting the internal ratings-based (IRB)
  approach. Therefore, total capital requirements depends not only on the portfolio's
  average PD but also on the shape of its PD distribution. Using a hand-collected
  dataset, I propose a method that decomposes the contribution of the PD distribution
  to capital requirements into an average component and a shape component. While a
  larger average component increases capital charges, a larger shape component generates
  capital savings. I investigate the relationship of these capital savings with the business cycle and find it to   be countercyclical. The results suggest that a recalibration of the current IRB framework can reduce considerably the procyclicality of capital regulation.
spacing: double
indent: true
subtitle: ''
thanks: Preliminary draft.
JEL: G21, G28, G11
urlcolor: black
toc: FALSE
---

@@

library(tidyverse)            ## Data manipulation, pipe operator
library(data.table)           ## Command to bind lists
library(ggridges)             ## Density ridges plot
library(stargazer)            ## Latex tables
library(lfe)                  ## High-dimensional fixed effects
library(gridExtra)            ## Create grid for plots and tables
library(cowplot)              ## Create grid for plots and tables
library(multipanelfigure)     ## Create grid for figures
library(DescTools)            ## Command to winsorize variables
library(ggpubr)               ## More plots
library(splitstackshape)      ## Command to expand data
library(latex2exp)            ## Use latex code in plots
library(lemon)                ## Plot brackets
library(mosaic)               ## Package to calculate derivatives
#library(textablr)
#library(sandwich)
#library(lmtest)
#library(relaimpo)            ## Calculate relative importance measures

@@

I find *Capital savings* to be countercyclical. I estimate that a 1.7% GDP growth rate (one standard deviation) decreases the growth rate of *Capital savings* by 0.8 percentage points on average. In other words, given an average PD, banks have to increase capital by 0.8 percentage points to keep their capital ratio constant. The effect is also economically significant. The variation of *Capital savings* during the business cycle reduces the procyclicality of capital ratio by 23.7% on average. The results also suggest that the countercyclical relationship between GDP and *Capital savings* is mostly driven by wholesale portfolios, especially corporate portfolios. The results are robust to different measures of the shape component, to the inclusion of several control variables and the alternative sample selections. I also show that selection into the IRB approach does not explain the cyclicality of *Capital savings*.

I further analyse the relationship of the PD distribution moments with GDP growth and find that during economic recessions average and variance of PD distributions increase while the their skewness decrease. Although the effect of the average PD is stronger, which characterizes capital requirements as procyclical, both the higher variance and the lower skewness of the PD distribution mitigate the increase of capital requirements during recessions. Moreover, I argue that the change of skewness during the business cycle is consistent with a portfolio reallocation effect on *Capital savings*.

@@

```{r, fig.height = 3, fig.width = 4,results="hide", fig.cap = pd_map_cap, fig.align = 'center', echo=FALSE, message=FALSE}
p <- ggplot(data = subset(data,subset = PD <0.2),
            mapping = aes(x = PD, y=K)) 
p + geom_line(alpha = 1) + 
  geom_segment(aes(x = PD.l, y = 0, xend = PD.l, yend = K.l), data = aux.df, linetype=3)+
  geom_segment(aes(x = PD.h, y = 0, xend = PD.h, yend = K.h), data = aux.df, linetype=3)+
  geom_segment(aes(x = PD.l, y = K.l, xend = PD.h, yend = K.h), data = aux.df, linetype=3)+
  geom_segment(aes(x = PD.a, y = K.a, xend = PD.a, yend = 0), data = aux.df, linetype=3)+
  geom_segment(aes(x = PD.a, y = K.s, xend = 0, yend = K.s), data = aux.df, linetype=3)+
  geom_segment(aes(x = PD.a, y = K.a, xend = 0, yend = K.a), data = aux.df, linetype=3)+

@@

```{r, include = TRUE, fig.height = 7.5, fig.width = 5,results="hide",fig.cap= savings_cap, fig.align = 'center'}
bank.data %>% filter(RWA.r.Total>0, bvdid %in% pillar3.data$bvdid)  %>% 
  select(name, Country, RWA.r.Total)%>%
  group_by(name, Country) %>%
#   summarise_if(is.numeric,median,na.rm= TRUE)%>%
  group_by(Country) %>%
 # mutate(order_aux = 1000*mean(RWA.r,na.rm = TRUE))%>%
  #ungroup()%>%
  #mutate(ordering = order_aux+RWA.r,
  #       name = as.factor(name),
  #       name = fct_reorder(name, ordering),
  #       Country = fct_reorder(Country, ordering)) %>%
 ggplot(mapping = aes(x = reorder(name, RWA.r.Total, FUN = mean, na.rm=TRUE),
                      y = RWA.r.Total)) +
geom_point(alpha = 0.5,size = 2) +
  stat_summary(fun.y="mean", geom="bar",alpha = 0.3) +
    labs(x=NULL) +
    coord_flip(ylim=c(1, 2.5)) +
  labs(y =  unname(TeX(c("$RWA^{s}$" )))) +
  scale_fill_grey()+
    theme_bw()

@@

```{r, include=TRUE, fig.height = 4, fig.width = 3,results="hide",fig.cap= savings_cap_country, fig.align = 'center'}
bank.data %>% filter(RWA.r.Total>0, bvdid %in% pillar3.data$bvdid) %>% 
  select(country.name,name, year, RWA.r.Total)%>%
  group_by(country.name,name) %>%
 summarise_if(is.numeric,mean,na.rm= TRUE)%>%
 ggplot(mapping = aes(x = reorder(country.name, RWA.r.Total, FUN = mean, na.rm=TRUE),
                          y = RWA.r.Total)) +
geom_point(alpha = 0.5,size = 2) +
  stat_summary(fun.y="mean", geom="bar",alpha = 0.3) +
    labs(x=NULL) +
  labs(y =  unname(TeX(c("$RWA^{s}" )))) +
  coord_flip(ylim=c(1, 2.5)) +
  theme_bw()

@@

```{r, include = TRUE, fig.height = 7.5, fig.width = 6,results="hide",fig.cap= savings_portfolio_cap, fig.align = 'center'}
bank.data %>% filter(RWA.r.Total>0, bvdid %in% pillar3.data$bvdid)  %>% 
  select(name, Country, RWA.r.Total, RWA.r.Retail, RWA.r.Wholesale)%>%
  pivot_longer(cols = c("RWA.r.Retail","RWA.r.Wholesale"), names_to = "Portfolio", values_to = "RWA.r") %>%
  mutate(Portfolio = factor(Portfolio, 
                            levels = c("RWA.r.Wholesale","RWA.r.Retail"), 
                            labels = c("Wholesale","Retail")))%>%
 ggplot(mapping = aes(x = reorder(name, RWA.r.Total, FUN = mean, na.rm=TRUE),
                      y = RWA.r)) +
geom_point(alpha = 0.5,size = 2) +
  stat_summary(fun.y="mean", geom="bar",alpha = 0.3) +
    labs(x=NULL) +
    coord_flip(ylim=c(1, 3.5)) +
  labs(y =  unname(TeX(c("$RWA^{s}$" )))) +
  scale_fill_grey()+
    theme_bw() +
  facet_wrap(~Portfolio)

@@

```{r, include = TRUE, fig.height = 7.5, fig.width = 6,results="hide",fig.cap= average_cap, fig.align = 'center'}
RW_summary <-  bank.data %>%
  mutate(RW.ranking = RW.IRB) %>%
  select(name, Country, RW.ranking, RW.s.Total, RW.hat.Total, RW.IRB)%>%
  pivot_longer(cols = c("RW.hat.Total","RW.s.Total","RW.IRB"), names_to = "Portfolio", values_to = "RW") %>%
  mutate(Portfolio = factor(Portfolio, 
                            levels = c("RW.s.Total", "RW.hat.Total", "RW.IRB"), 
                            labels = c("j = s","j = c", "j = f")))%>%
  group_by(Portfolio) %>%
  dplyr::summarize(mean = round(mean(RW, na.rm = TRUE),2),
            sd   = round(sd(RW, na.rm = TRUE),2)) %>%
  mutate(lab = paste("Mean = ", mean, "\n St. Dev. = ", sd, sep = ""))

bank.data %>% filter(RWA.r.Total>0, bvdid %in% pillar3.data$bvdid)  %>% 
  mutate(RW.ranking = RW.IRB) %>%
  select(name, Country, RW.ranking, RW.s.Total, RW.hat.Total, RW.IRB)%>%
  pivot_longer(cols = c("RW.hat.Total","RW.s.Total","RW.IRB"), names_to = "Portfolio", values_to = "RW") %>%
  mutate(Portfolio = factor(Portfolio, 
                            levels = c("RW.s.Total", "RW.hat.Total", "RW.IRB"), 
                            labels = c("j = s","j = c", "j = f")))%>%
 ggplot(mapping = aes(x = reorder(name, RW.ranking, FUN = mean, na.rm=TRUE),
                      y = RW)) +
geom_point(alpha = 0.5,size = 2) +
  stat_summary(fun.y="mean", geom="bar",alpha = 0.3) +
    labs(x=NULL) +
    coord_flip() +
  labs(y =  unname(TeX(c("$RW^{j}$" )))) +
  scale_fill_grey()+
    theme_bw() +
  facet_wrap(~Portfolio)+
  geom_text(data = RW_summary, aes(label = lab), x = 3, y = 0.85, size=3.5)

@@

```{r}
derivatives = "\\label{fig:derivatives} The figure plots risk-weights as a function of probability of default (top-left) and its first, second, and third derivative with respect to probability of default (top-right, bottom-left, and bottom-right, respectively)."
```
```{r, fig.cap= derivatives, fig.align="center"}
p1 <- ggdraw() + draw_image("../../Auxiliar/Pictures/function.jpg", scale = 0.9)
p2 <- ggdraw() + draw_image("../../Auxiliar/Pictures/first_derivative.jpg", scale = 0.9)
p3 <- ggdraw() + draw_image("../../Auxiliar/Pictures/second_derivative.jpg", scale = 0.9)
p4 <- ggdraw() + draw_image("../../Auxiliar/Pictures/third_derivative.jpg", scale = 0.9)

@@

```{r, fig.height = 6, fig.width = 6, results="hide",fig.cap= densities, include=TRUE}

@@

 pillar3.data %>%
 select(name, PD, EAD, Portfolio_2, Portfolio_1) %>%
  filter(EAD>0, PD<1, Portfolio_2 %in% c("Banks", "Corporate", "Sovereign") | Portfolio_1 %in% c("Retail"))%>%
  mutate(Portfolio = ifelse(Portfolio_1 == "Retail", "Retail", as.character(Portfolio_2)),
         EAD = round(EAD/10),
         PD = ifelse(PD>0.25, 0.25, PD)) %>%
  na.omit(cols=c("EAD", "Portfolio")) %>%
  expandRows("EAD")%>%
  ggplot(mapping = aes(x = PD)) +
    geom_histogram(aes(y=..density..), bins = 50)+
  labs(x=NULL, y= NULL) +
   theme_bw() +
  theme(panel.grid.minor = element_blank())+
  scale_fill_grey() +
  facet_wrap(~ Portfolio) +
  geom_text(data = PD_summary, aes(label = lab), x = 0.15, y = 150)

>>>>

---
title: "The Countercyclical Component of Capital Regulation"
date: '\emph{\today}'
output:
  bookdown::pdf_document2:
    fig_caption: yes
    #citation_package: natbib
    latex_engine: pdflatex
    template: tex-ms.tex
  pdf_document: default
  word_document: default
author:
- name: "Lucas Avezum"
  affiliation: "CentER and EBC, Tilburg University"
biblio-style: apsr
bibliography: ../../Auxiliar/mybibfile.bib
citecolor: black
csl: ../../Auxiliar/Citation_styles/american-marketing-association.csl
#anonymous: no
fontsize: 11pt
geometry: margin= 1in
header-includes: \usepackage{rotating, graphicx, dcolumn, longtable, float, siunitx, tabularx, appendix} 
keywords: Internal ratings-based models, Risk-weighted assets dispersion, Procyclicality
linkcolor: black
abstract: The Basel II accord introduced a concave mapping from probabilities of default
  (PD) to capital requirements for banks adopting the internal ratings-based (IRB)
  approach. Therefore, total capital requirements depends not only on the portfolio's
  average PD but also on the shape of its PD distribution. Using a hand-collected
  dataset, I propose a method that decomposes the contribution of the PD distribution
  to capital requirements into an average component and a shape component. While a
  larger average component increases capital charges, a larger shape component generates
  capital savings. I investigate the relationship of these capital savings with the business cycle and find it to   be countercyclical. The results suggest that a recalibration of the current IRB framework can reduce considerably the procyclicality of capital regulation.
spacing: double
indent: true
subtitle: ''
thanks: Preliminary draft.
JEL: G11, G21, G28 
urlcolor: black
toc: FALSE
---

@@

library(tidyverse)            ## Data manipulation, pipe operator
library(data.table)           ## Command to bind lists
library(ggridges)             ## Density ridges plot
library(stargazer)            ## Latex tables
library(lfe)                  ## High-dimensional fixed effects
library(gridExtra)            ## Create grid for plots and tables
library(cowplot)              ## Create grid for plots and tables
library(multipanelfigure)     ## Create grid for figures
library(DescTools)            ## Command to winsorize variables
library(ggpubr)               ## More plots
library(splitstackshape)      ## Command to expand data
library(latex2exp)            ## Use latex code in plots
library(lemon)                ## Plot brackets
#library(mosaic)               ## Package to calculate derivatives
#library(textablr)
#library(sandwich)
#library(lmtest)
#library(relaimpo)            ## Calculate relative importance measures

@@

I find *Capital savings* to be countercyclical. I estimate that a 1.7% GDP growth rate (one standard deviation) decreases the growth rate of *Capital savings* by 0.8 percentage points on average. In other words, given an average PD, banks have to increase capital by 0.8 percentage points to keep their capital ratio constant. The effect is also economically significant. The variation of *Capital savings* during the business cycle reduces the procyclicality of capital ratio by 23.7% on average. The results also suggest that the countercyclical relationship between GDP and *Capital savings* is mostly driven by wholesale portfolios, especially corporate portfolios. The results are robust to different measures of the shape component, to the inclusion of several control variables and alternative sample selections. I also show that selection into the IRB approach does not explain the cyclicality of *Capital savings*.

I further analyse the relationship of the PD distribution moments with GDP growth and find that during economic recessions the average and the variance of PD distributions increase while the their skewness decrease. Although the effect of the average PD is stronger, which characterizes capital requirements as procyclical, both the higher variance and the lower skewness of the PD distribution mitigate the increase of capital requirements during recessions. Moreover, I argue that the change of skewness during the business cycle is consistent with a portfolio reallocation effect on *Capital savings*.

@@

```{r mapping, fig.height = 3, fig.width = 4,results="hide", fig.cap = pd_map_cap, fig.align = 'center', echo=FALSE, message=FALSE}
p <- ggplot(data = subset(data,subset = PD <0.2),
            mapping = aes(x = PD, y=K)) 
p + geom_line(alpha = 1) + 
  geom_segment(aes(x = PD.l, y = 0, xend = PD.l, yend = K.l), data = aux.df, linetype=3)+
  geom_segment(aes(x = PD.h, y = 0, xend = PD.h, yend = K.h), data = aux.df, linetype=3)+
  geom_segment(aes(x = PD.l, y = K.l, xend = PD.h, yend = K.h), data = aux.df, linetype=3)+
  geom_segment(aes(x = PD.a, y = K.a, xend = PD.a, yend = 0), data = aux.df, linetype=3)+
  geom_segment(aes(x = PD.a, y = K.s, xend = 0, yend = K.s), data = aux.df, linetype=3)+
  geom_segment(aes(x = PD.a, y = K.a, xend = 0, yend = K.a), data = aux.df, linetype=3)+

@@

```{r savings_by_bank, include = TRUE, fig.height = 5.5, fig.width = 4,results="hide",fig.cap= savings_cap, fig.align = 'center'}
bank.data %>% filter(RWA.r.Total>0, bvdid %in% pillar3.data$bvdid)  %>% 
  select(name, Country, RWA.r.Total)%>%
  group_by(name, Country) %>%
#   summarise_if(is.numeric,median,na.rm= TRUE)%>%
  group_by(Country) %>%
 # mutate(order_aux = 1000*mean(RWA.r,na.rm = TRUE))%>%
  #ungroup()%>%
  #mutate(ordering = order_aux+RWA.r,
  #       name = as.factor(name),
  #       name = fct_reorder(name, ordering),
  #       Country = fct_reorder(Country, ordering)) %>%
 ggplot(mapping = aes(x = reorder(name, RWA.r.Total, FUN = mean, na.rm=TRUE),
                      y = RWA.r.Total)) +
geom_point(alpha = 0.5,size = 1) +
  stat_summary(fun.y="mean", geom="bar",alpha = 0.3, aes(width=0.6)) +
    labs(x=NULL) +
    coord_flip(ylim=c(1, 2.5)) +
  labs(y =  unname(TeX(c("$RWA^{s}$" )))) +
  scale_fill_grey()+
    theme_bw()+
  theme(text = element_text(size=8))

@@

```{r savings_by_country, include=TRUE, fig.height = 3, fig.width = 3,results="hide",fig.cap= savings_cap_country, fig.align = 'center'}
bank.data %>% filter(RWA.r.Total>0, bvdid %in% pillar3.data$bvdid) %>% 
  select(country.name,name, year, RWA.r.Total)%>%
  group_by(country.name,name) %>%
 summarise_if(is.numeric,mean,na.rm= TRUE)%>%
 ggplot(mapping = aes(x = reorder(country.name, RWA.r.Total, FUN = mean, na.rm=TRUE),
                          y = RWA.r.Total)) +
geom_point(alpha = 0.5,size = 2) +
  stat_summary(fun.y="mean", geom="bar",alpha = 0.3) +
    labs(x=NULL) +
  labs(y =  unname(TeX(c("$RWA^{s}" )))) +
  coord_flip(ylim=c(1, 2.5)) +
  theme_bw()

@@

```{r savings_by_portfolio, include = TRUE, fig.height = 5.5, fig.width = 5,results="hide",fig.cap= savings_portfolio_cap, fig.align = 'center'}

RW_summary <-  bank.data %>%ungroup()%>%
  select(name, Country, RWA.r.Total, RWA.r.Retail, RWA.r.Wholesale)%>%
  dplyr::summarise(across(c("RWA.r.Retail","RWA.r.Wholesale"), 
                          ~round(cor(RWA.r.Total,., use="complete.obs"),2),))%>%
  pivot_longer(cols = everything(), names_to = "Portfolio", values_to = "Corr")%>%
   mutate(Portfolio = factor(Portfolio, 
                            levels = c("RWA.r.Wholesale","RWA.r.Retail"), 
                            labels = c("Wholesale","Retail")))%>%
  mutate(lab = paste("Correlation = ", Corr, sep = ""))

bank.data %>% filter(RWA.r.Total>0, bvdid %in% pillar3.data$bvdid)  %>% 
  select(name, Country, RWA.r.Total, RWA.r.Retail, RWA.r.Wholesale)%>%
  pivot_longer(cols = c("RWA.r.Retail","RWA.r.Wholesale"), names_to = "Portfolio", values_to = "RWA.r") %>%
  mutate(Portfolio = factor(Portfolio, 
                            levels = c("RWA.r.Wholesale","RWA.r.Retail"), 
                            labels = c("Wholesale","Retail")))%>%
 ggplot(mapping = aes(x = reorder(name, RWA.r.Total, FUN = mean, na.rm=TRUE),
                      y = RWA.r)) +
geom_point(alpha = 0.5,size = 1) +
  stat_summary(fun.y="mean", geom="bar",alpha = 0.3, aes(width=0.6)) +
    labs(x=NULL) +
    coord_flip(ylim=c(1, 3.5)) +
  labs(y =  unname(TeX(c("$RWA^{s}$" )))) +
  scale_fill_grey()+
    theme_bw() +
  theme(text = element_text(size=8))+
  facet_wrap(~Portfolio)
#+
 # geom_text(data = RW_summary, aes(label = lab), x = 4, y = 2.8, size=2.5)

@@

```{r decomposition, include = TRUE, fig.height = 5.5, fig.width = 5,results="hide",fig.cap= average_cap, fig.align = 'center'}
RW_summary <-  bank.data %>%
  mutate(RW.ranking = RW.IRB) %>%
  select(name, Country, RW.ranking, RW.s.Total, RW.hat.Total, RW.IRB)%>%
  pivot_longer(cols = c("RW.hat.Total","RW.s.Total","RW.IRB"), names_to = "Portfolio", values_to = "RW") %>%
  mutate(Portfolio = factor(Portfolio, 
                            levels = c("RW.s.Total", "RW.hat.Total", "RW.IRB"), 
                            labels = c("j = s","j = c", "j = f")))%>%
  group_by(Portfolio) %>%
  dplyr::summarize(mean = round(mean(RW, na.rm = TRUE),2),
            sd   = round(sd(RW, na.rm = TRUE),2)) %>%
  mutate(lab = paste("Mean = ", mean, "\n St. Dev. = ", sd, sep = ""))

bank.data %>% filter(RWA.r.Total>0, bvdid %in% pillar3.data$bvdid)  %>% 
  mutate(RW.ranking = RW.IRB) %>%
  select(name, Country, RW.ranking, RW.s.Total, RW.hat.Total, RW.IRB)%>%
  pivot_longer(cols = c("RW.hat.Total","RW.s.Total","RW.IRB"), names_to = "Portfolio", values_to = "RW") %>%
  mutate(Portfolio = factor(Portfolio, 
                            levels = c("RW.s.Total", "RW.hat.Total", "RW.IRB"), 
                            labels = c("j = s","j = c", "j = f")))%>%
 ggplot(mapping = aes(x = reorder(name, RW.ranking, FUN = mean, na.rm=TRUE),
                      y = RW)) +
geom_point(alpha = 0.5,size = 1) +
  stat_summary(fun.y="mean", geom="bar",alpha = 0.3, aes(width=0.6)) +
    labs(x=NULL) +
    coord_flip() +
  labs(y =  unname(TeX(c("$RW^{j}$" )))) +
  scale_fill_grey()+
    theme_bw() +
  theme(text = element_text(size=8))+
  facet_wrap(~Portfolio)+
  geom_text(data = RW_summary, aes(label = lab), x = 3, y = 0.85, size=2.5)

@@

```{r}
derivatives = "\\label{fig:derivatives} The figure plots risk-weights as a function of probability of default (top-left) and its first, second, and third derivative with respect to probability of default (top-right, bottom-left, and bottom-right, respectively)."
```
```{r derivatives, fig.cap= derivatives, fig.align="center", fig.width = 5}
p1 <- ggdraw() + draw_image("../../Auxiliar/Pictures/function.jpg", scale = 0.9)
p2 <- ggdraw() + draw_image("../../Auxiliar/Pictures/first_derivative.jpg", scale = 0.9)
p3 <- ggdraw() + draw_image("../../Auxiliar/Pictures/second_derivative.jpg", scale = 0.9)
p4 <- ggdraw() + draw_image("../../Auxiliar/Pictures/third_derivative.jpg", scale = 0.9)

@@

```{r densities, fig.height = 5, fig.width = 5, results="hide",fig.cap= densities, include=TRUE}

@@

 pillar3.data %>%
 select(name, PD, EAD, Portfolio_2, Portfolio_1) %>%
  filter(EAD>0, PD<1, Portfolio_2 %in% c("Banks", "Corporate", "Sovereign") | Portfolio_1 %in% c("Retail"))%>%
  mutate(Portfolio = ifelse(Portfolio_1 == "Retail", "Retail", as.character(Portfolio_2)),
         EAD = round(EAD/10),
         PD = ifelse(PD>0.25, 0.25, PD)) %>%
  na.omit(cols=c("EAD", "Portfolio")) %>%
  expandRows("EAD")%>%
  ggplot(mapping = aes(x = PD)) +
    geom_histogram(aes(y=..density..), bins = 50)+
  labs(x=NULL, y= NULL) +
   theme_bw() +
  theme(panel.grid.minor = element_blank())+
  scale_fill_grey() +
  facet_wrap(~ Portfolio) +
  geom_text(data = PD_summary, aes(label = lab), x = 0.15, y = 150, size=2.5)
